Cultural Transmission Can Explain the Evolution of Cooperation

### 2020-08-08 ms/main.tex
Adjust the figures as youav asked

\begin{figure}[htb]
  \centering
    \includegraphics[scale=1]{figure2a.pdf}
    \includegraphics[scale=1]{figure2b.pdf}
  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or fixation depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow). The blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, $c$ and $T_B$ vary on the y- and x-axes. \textbf{Left}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow). \textbf{Right}: With $\alpha=0$, coexistence is not possible.}
    \label{fig:results2}
\end{figure}
%%%

%%% Figure: coexistence map
\begin{figure}[htb]
\centering
\includegraphics[scale=1]{coexistence.pdf}
\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$. The line of $\hat{p}'=p$ is in orange. The curve and line intersect at the equilibrium $\hat{p}^*$. 
The blue curve is above the orange line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$. The blue curve is below the orange line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
}
\label{fig:coexistence}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
    \includegraphics[scale=1]{figure2a.pdf}
    \includegraphics[scale=1]{figure2b.pdf}
  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or fixation depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow). The blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, $c$ and $T_B$ vary on the y- and x-axes. \textbf{Up}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow). \textbf{Down}: With $\alpha=0$, coexistence is not possible.}
    \label{fig:results2}
\end{figure}
%%%

%%% Figure: coexistence map
\begin{figure}[htb]
\centering
\includegraphics[scale=1]{coexistence.pdf}
\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$. The line of $\hat{p}'=\hat{p}$ is in dashed black. The curve and dashed line intersect at the equilibrium $\hat{p}^*$. 
The blue curve is above the black dashed line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$. The blue curve is below the orange line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
}
\label{fig:coexistence}
\end{figure}
